Magic-free Code Extraction of Generic Programs and Recursion Schemes in Coq

### 2024-03-18 paper/paper.tex
minor

\subsection{Functors and Containers}
\label{sec:containers}
Functors are functions \coq{F : Type -> Type} which additionally have a
map \coq{fmap : forall A B, (A -> B) -> F A -> F B} witnessing the idea that a
functor represents a container for abstract data that can be manipulated without
changing the outer structure. For example, the type \coq{List : Type -> Type} is
a functor and \coq{List A} is the type of lists over elements of type \coq{A}
with the obvious \coq{fmap} function recursively traversing a list and applying
the function \coq{A -> B} for each element. Additionally, the type of
lists \coq{List A} arises as the least fixed-point of the
functor \coq{F X = unit + (A * X) }.

>>>>

\subsection{Functors and Containers}
\label{sec:containers}
Functors are functions \coq{F : Type -> Type} which additionally have a
map
\begin{coqcode}
fmap : forall A B, (A -> B) -> F A -> F B
\end{coqcode}
witnessing the idea that a
functor represents a container for abstract data that can be manipulated without
changing the outer structure. For example, the type \coq{List : Type -> Type} is
a functor and \coq{List A} is the type of lists over elements of type \coq{A}
with the obvious \coq{fmap} function recursively traversing a list and applying
the function \coq{A -> B} for each element. Additionally, the type of
lists \coq{List A} arises as the least fixed-point of the
functor \coq{F X = unit + (A * X) }.
